---
title: "Trends in U.S. oyster landings"
subtitle: "Volume and inflation-adjusted prices 1950 - 2024"
author: "Jorge Schmidt"
institute: "Rosenstiel School of Marine, Atmospheric, and Earth Science, Univertsity of Miami"
date: "11/27/2025
format: html
---

## Introduction

This repository contains data and code to build a dataset of landings of fresh 
oysters from 1950 to 2024, inclusive, calculates weighed-average 
inflation-adjusted prices, and breaks out data for the top five producing states. It includes and aggregates all reported oyster species in NOAA records.

## Objectives

It is intended to support decision-making in the oyster production and distribution sectors by displaying trends in volumes and prices.

## Data Sources

The data for oyster landings volumes and historical prices comes from NOAA. The
data to calculate the adjustments for inflation comes from the St. Louis Fed (FRED).

## Data Processing

1. The file from NOAA contains 1,767 yearly observations (rows) and 11 columns (year + 10 variables). Some of the data is redundant (common and scientific names, and tsn), adds imprecision (metric tons and lbs), or is irrelevant for the purposes of this analysis (collection, confidentiality, source).

2. The file from FRED contains 908 monthly observations (rows) and two columns (date and CPI value).

3. Clean up, filter, and export the data from NOAA and the St. Louis Fed.
2. 

## 

## Main Findings

```{r}
 # Load packages 
library(here)
```

## References

 - The landings data [FOSS_landings.xlsx] was obtained from
 https://www.fisheries.noaa.gov/foss/f?p=215:200:7482903932446

 - The inflation data [CPIAUCSL.csv] was obtained from
https://fred.stlouisfed.org/series/CPIAUCSL


When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this 

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).



(50%) Have the following section headers / slides: Introduction1, Objective(s)2, Data sources3, Data processing4, Main findings5, and References6. Each section should have a brief description. One paragraph may be enough, but feel free to write as much as you need to.
(10%) You include at least two figures7:
One of those must be the map from Assignment 4. The other one may be one from Assignment 3, or a figure that you generate directly in the document.
All figures should include a figure caption.8
(5%) You must use inline code at least once to present information from your data.
